resistanceModelNotesAndy

### 2015-06-10 resistanceModelNotesAndy.Rmd
notes

@@

@@

1. Questions for Ian
+ do we want to do sequential & mixtures for the first sensitivity analysis ?
+ what are the maximum generations that we are running for ? How do we deal with runs where critical point isn't reached in max generations.
+ is it OK to asses just resistance in males ?

1. write out how I'm going to run the sensitivity analysis so I can do a final check with Ian while I'm in Liverpool.

1. think about whether we are able to run sequential insecticide scenarios with the current setup.

1. be careful that runModel & runModel2 should no longer generate same results when sex linkage is set (but i don't think this should break current testthat tests)

>>>>

be careful that runModel & runModel2 should no longer generate same results when sex linkage is set (but i don't think this should break current testthat tests)

@@

** 10/6/15 ** train back from liverpool

modifying sensiAnPaper1() to run the different insecticideUsed scenarios
started sensiPostProc() to do post-processing

@@

1. work on sensiPostProc() It will need to be quite clever. It will take the output files from insecticide1, insecticide2 and mixture and use these to calculate timeToResistance critical points for sequential, mixture1 & mixture2 scenarios.

1. do the output files from runModel2() have the input params attached or do I need to save inputs & outputs separately ? The latter may be a good plan to avoid having to rerun long simulations if I want to investigate outputs further later.

1. maybe rename sensiAnPaper1 to something more informative
